MASU Paper

### 2022-05-18 paper/paper_draft.Rmd
MASU paper with updated discussion section

<!-- What did we do and find? -->
<!-- 	Thesis -->
Due to the history of hydrologic modifications such as the development of reservoirs, dams, and irrigation systems, there has been an apparent decrease in the number of migratory fishes in the recent years. For example, on the Pacific coast there has been significant decreases in diversity within salmonid species due hydrologic and dam alterations. Atlantic salmon and anadromous species of sturgeons are also impacted negatively because of a loss of portions to their habitats upstream of dams. Overall, the diversity within migratory fish species have largely declined due to these dams blocking the fishes' migratory paths. One species of migratory fish that we will be discussing more in depth is the MASU salmon.

@@

```{r, echo=FALSE, include=FALSE}
dat<-read.table("../data/genotypes.geno")                        
meta<- read.table("../data/sample_meta.txt", header=TRUE)
snp.meta<- dat[,1:2]
colnames(snp.meta)<- c("chr", "position")
library(snpR)
dat<- import.snpR.data(dat[,-c(1:2)], snp.meta = snp.meta, sample.meta = meta)
dat<- filter_snps(dat, maf = 0.05, hwe = 0.000001)
number_snps_after_filtering <- nsnps(dat)

@@

<!-- Will need to fill in NGSadmix -->

@@

>>>>

<!-- What did we do and find? -->
<!-- 	Thesis -->

Due to the history of hydrologic modifications such as the development of reservoirs, dams, and irrigation systems, there has been an apparent decrease in the number of migratory fishes in the recent years. For example, on the Pacific coast there has been significant decreases in diversity within salmonid species due hydrologic and dam alterations. Atlantic salmon and anadromous species of sturgeons are also impacted negatively because of a loss of portions to their habitats upstream of dams. Overall, the diversity within migratory fish species have largely declined due to these dams blocking the fishes' migratory paths. One species of migratory fish that we will be discussing more in depth is the MASU salmon.

@@

<!-- Anadromous salmon -> dams causing them to not be able to jump over dams -> is we explore the genetic influences of anadromy and residents in MASU salmon then we can tell where to focus our conservation efforts. -->

<!-- Parr size was generally larger and maturation was more common at more southern latitudes -->

<!-- Population density and temperature two most important factors affecting the growth of the fish.  -->

<!-- superior development promotes residency (early maturation) -->

<!-- need to do citations -->
```{r, echo=FALSE, include=FALSE}
dat<-read.table("../data/genotypes.geno")                        
meta<- read.table("../data/sample_meta.txt", header=TRUE)
snp.meta<- dat[,1:2]
colnames(snp.meta)<- c("chr", "position")
library(snpR)
dat<- import.snpR.data(dat[,-c(1:2)], snp.meta = snp.meta, sample.meta = meta)
dat<- filter_snps(dat, maf = 0.05, hwe = 0.000001)
number_snps_after_filtering <- nsnps(dat)

@@

@@

# Discussion 
## Results Discussion
According to the PCA, there is overlap between the anadromous and resident individuals from both populations. In other words, there are not clear distinct clusters that separate the anadromous individuals from the resident individuals. This indicates there is not strong evidence for a genetic influence that determines the MASU salmon's life cycle.

## Ramifications for MASU salmon
In these populations it is possible that residency and anadromy within MASU salmon are not solely genetically controlled and that we must take into consideration the environmental influences. When comparing MASU salmon to steelhead, steelhead and their life cycles are more heavily influenced by genetic factors. As of now, MASU salmon and their life cycles are mainly influenced my environmental factors, but further studies with larger sample sizes would need to be conducted in order to see if any genetic influences play a role. In other words, we would need still need to figure out if MASU salmon life cycles are influenced by the additive effects of genetics and environment, the multiplying effetcs of genetics and environment, or simply a result of purely environmental effects.

## Ramifications for Salmonids in General 
In terms of the importance of this work, figuring out if MASU salmon life cycles have genetics influences will go towards their conservation efforts. For example, within steelhead fish, anadromous individuals will have to migrate upstream in order to move towards the ocean. On some occurrences the anadromous steelhead will be stopped midway towards their journey to the ocean due to manmade dams. This has caused a reduction in diversity within these fish by causing an apparent increase in resident individuals within the population. Knowing whether a fish is anadromous or resident would be helpful because people can advocate for dams to built in areas where there are a lot of anadromous fish. This same logic can also be applied towards the conservation of MASU salmon.
